Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-03-03 WSSSPE2_report/WSSSPE2_review.tex
Section 3: Intro.

\todo{Live notes at \url{http://tinyurl.com/q6ew45v}.
%https://docs.google.com/document/d/1-BxkYWDQ6nNNBXBStUL0xcKF9qCTlEALwf928J_MemI/edit?usp=sharing
Abstracts at \url{http://tinyurl.com/mnenzms}}

>>>>

\todo{Live notes at \href{http://tinyurl.com/q6ew45v}{Google Notes}.
%https://docs.google.com/document/d/1-BxkYWDQ6nNNBXBStUL0xcKF9qCTlEALwf928J_MemI/edit?usp=sharing
Abstracts at \href{http://tinyurl.com/mnenzms}{WSSSPE2}.}

The workshop featured two keynote addresses. In the opening keynote
presentation, Kaitlin Thaney of Mozilla Science talked about her organization's
work and policy to enable and support sustainable and reproducible scientific
research. Our second keynote speaker was Neil Chue Hong of Software
Sustainability Institute. He shined the light on how scientific software is
prevalently driving advances in many sciences and engineering fields. Following
the keynotes, participants broke into groups to define and discuss the crucial
notion ``sustanability'' spawned by the speeches of our keynote speakers as well
as the theme of our workshop.
